Proposed Solution

### 2017-04-17 OOPSLA17/secs/eval.tex
finish related work paragraph for sequential pattern mining

The resulting false positive rate is then estimated to be 11\%-18\%.
This is in the range of existing work, for example in the EnCore tool, which had a false positive rate of 13\%,21\%,32\% for MySQL, Apache, and PHP respectively~\cite{encore}.
We note again that as opposed to a tool like EnCore, which is used mainly to detect initialization errors, thanks to the complex relations that can be learned, \app also learns misconfigurations causing runtime performance degradation.
This means \app generates a larger rule set, and false positives cannot be garunteed, i.e. there may be some environment conditions that will cause a ``false'' positive to become a true positive.

In contrast, a true positive can be confirmed as such based on evidence of unwanted system behvaior.
The errors listed in Table~\ref{table-casestudy} are confirmed true positives, evidenced by posts on help forums.
\app detected and reports these errors in the 15 code repositories listed in the URL column of Table~\ref{table-casestudy}. 
These are real-world configuration files that contain errors that may be unknown to the maintainers of the repositories.
%The errors were not submitted as patches to the repository owners, since it is possible the owner of the repository has a user case for this configuration file that will not trigger the unwanted behavior.

>>>>

The resulting false positive rate is then estimated to be 11\%-18\%.
This is in the range of existing work, for example in the EnCore tool, which had a false positive rate of 13\%,21\%,32\% for MySQL, Apache, and PHP respectively~\cite{encore}.
We note again that as opposed to a tool like EnCore, which is used mainly to detect initialization errors, thanks to the complex relations that can be learned, \app also learns misconfigurations causing runtime performance degradation.
This means \app generates a larger rule set, and false positives cannot be guaranteed, \ie there may be some environment conditions that will cause a ``false'' positive to become a true positive.

In contrast, a true positive can be confirmed as such based on evidence of unwanted system behavior.
The errors listed in Table~\ref{table-casestudy} are confirmed true positives, evidenced by posts on help forums.
\app detected and reports these errors in the 15 code repositories listed in the URL column of Table~\ref{table-casestudy}. 
These are real-world configuration files that contain errors that may be unknown to the maintainers of the repositories.
%The errors were not submitted as patches to the repository owners, since it is possible the owner of the repository has a user case for this configuration file that will not trigger the unwanted behavior.

### 2017-04-17 OOPSLA17/secs/related.tex
finish related work paragraph for sequential pattern mining

\para{Misconfiguration diagnosis}
Many misconfiguration diagnosis approaches have been proposed%
~\cite{attariyan10automating, attariyan12x-ray}.
For example, ConfAid~\cite{attariyan10automating} 
and X-ray~\cite{attariyan12x-ray} use dynamic information
flow tracking to find possible configuration errors that may result in
failures or performance problems. AutoBash~\cite{su07autobash} 
tracks causality and automatically fixes 
misconfigurations. Unlike \app, most misconfiguration
diagnosis efforts aim at finding errors after system
failures occur, which leads to prolonged recovery time.

>>>>

\para{Misconfiguration diagnosis}
Misconfiguration diagnosis approaches have been proposed to address configuration problems post-mortem.
For example, ConfAid~\cite{attariyan10automating} 
and X-ray~\cite{attariyan12x-ray} use dynamic information
flow tracking to find possible configuration errors that may have resulted in
failures or performance problems. AutoBash~\cite{su07autobash} 
tracks causality and automatically fixes 
misconfigurations. Unlike \app, most misconfiguration
diagnosis efforts aim at finding errors after system
failures occur, which leads to prolonged recovery time.

\para{Association Rule Learning}
The approach we have presented not only generalizes association rule learning, but also another learning strategy called \textit{sequential pattern mining}~\cite{mabroukeh2010taxonomy}. Ordering rules are similar to the patterns learned in sequential pattern mining, although we restrict our ordering rules to $|S|,|T|=1$ since these are the most common misconfigurations we encounter in practice.
While a major limitation to sequential pattern mining is the scalability of the problem~\cite{ayres2002sequential}, we escape this issue with $|S|,|T|=1$ and the fact that a single configuration file tends to be less a few thousand lines.
There has been other work in these same classes of algorithms~\cite{han2007frequent,langley1995applications} for various applications and variations on the core problem.
A future direction for this work is to integrate advances in these domains into the configuration file verification problem.
